Cluster Paper

### 2015-03-30 ms.tex
clean up outline

\section{MOCK CATALOGS}
\subsection{Input Simulations}

\section{MOCK OBSERVATIONS}

@@

\subsection{Velocity Dispersion}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

@@

@@

\subsection{Halo Mass}

\editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}

\subsection{Substructure}

\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}

\section{RESULTS}
\subsection{Cluster Number}
\subsection{Membership \& Cluster Masses}

>>>>

\section{AARDVARK SIMULATION}

\section{THE HETDEX SURVEY}

@@

\subsection{Mock Observations}

\subsection{Dynamical Properties}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

@@

For the mass \editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}.

\subsection{Structural Properties}
\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}

@@

\section{RESULTS}
